---
title: "Solution_chap3"
author: "Sergio Ibarra-Espinosa"
date: "2024-03-09"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1) Exercisice

3.1) Using R, install the package vein and run the following script. The idea is to
compare how the emission varies depending on speed. What can be
concluded? Do the emission factors converge to some speed? Analyze different
pollutants. The resulting emission factors give units of g/km. Then, multiply by
different distances (your house to school/work, for instance) and estimate
emissions.

```{r}
library(vein)
ef1 <- ef_eea(category = "PC", 
              fuel = "G",  
              segment = "Small", 
              euro = "III", 
              tech = "GDI",  
              pol = "NOx", 
              mode = NA,
              slope = 0, 
              load = 0)

ef2 <- ef_eea(category = "PC", 
              fuel = "G",  
              segment = "Small", 
              euro = "I", 
              tech = NA,  
              pol = "NOx", 
              mode = NA,
              slope = 0, 
              load = 0)
df <- data.frame(EF_Euro_III = ef1(0:100), 
                 EF_Euro_I = ef2(0:100))
colplot(df, main = "NOx (g/km)" , xlab = "Speed (km/h)")
```

### What can be concluded? 

> **_ANSWER:_**  On average, the vehicle Euro I emits more emissions 
at low and high speeds. However, the Euro III 
emits less emissions at higher and speeds. 
This represent a scenario without stops and and flat terrain.


### Do the emission factors converge to some speed? 

> **_ANSWER:_**  Not in this case.


### Analyze different pollutants. 


```{r}
library(vein)
ef1 <- ef_eea(category = "PC", 
              fuel = "G",  
              segment = "Small", 
              euro = "III", 
              tech = "GDI",  
              pol = "CO", 
              mode = NA,
              slope = 0, 
              load = 0)

ef2 <- ef_eea(category = "PC", 
              fuel = "G",  
              segment = "Small", 
              euro = "I", 
              tech = NA,  
              pol = "CO", 
              mode = NA,
              slope = 0, 
              load = 0)
df <- data.frame(EF_Euro_III = ef1(0:100), 
                 EF_Euro_I = ef2(0:100))
colplot(df, main = "CO (g/km)", xlab = "Speed (km/h)")
```

> **_ANSWER:_**  When analyzing the CO emission factors, we see that lower
speeds, the Euro I emits more pollution than Euro III. For instance,
when the speed is lower than 10km/h, Euro I emits, 9 times more than a vehicle
Euro III.


### The resulting emission factors give units of g/km. Then, multiply by
different distances (your house to school/work, for instance) and estimate
emissions.


> **_ANSWER:_**  If we asume that the distance between my school and 
home is 1 km in a straight line, we commute in a gasoline vehicle Euro III at 
speed of 40 km/h, the vehicle would emit 0.52 g of CO. 

```{r}
round(ef1(40), 2)
```

